\section{Introduction}\label{sec:introduction}
Large language model (LLM) applications such as ChatGPT~\cite{chatgpt}, Gemini~\cite{gemini}, and Claude~\cite{claude} increasingly incorporate web search functions, providing internet users with new ways of accessing information~\cite{webgpt-arxiv21, geo-apmr+24, zhai2024llm-and-future-of-information-retrieval}. 
Information retrieval has become a primary use case for LLMs, with a survey showing that about $30\%$ of all prompts involve information seeking~\cite{how-people-use-chatgpt-nber25}. 
Such systems that perform web searches and generate textual answers based on users' needs and backgrounds are known as \emph{generative search engines} (GSEs)~\cite{geo-apmr+24}. 
Web search services are rapidly transitioning from traditional search engines to GSE-based systems~\cite{openai-chatgpt-search24, google-gemini-search24, perplexity-comet25, dia-browser25, microsoft-bing-chat23, anthropic-multiagent25}, changing the way users access and interpret web content.

% GSEs not only alter the delivery of information but also reshape its nature. 
% Whereas conventional search engines direct users to primary information sources such as official documents, GSEs provide synthesized answers that summarize, interpret, and personalize web content. 
% LLMs also exhibit bias~\cite{bias-and-fairness-in-large-language-models-cl24, on-the-dangers-of-stochastic-parrots-facc21, holisticevaluationlanguagemodels-arxiv22, bbc-ai-search-engines-2024}, meaning that users receive secondary or higher-order information produced by LLMs~\cite{the-spread-of-true-and-false-news-online-science2018}.
% This transformation enhances accessibility but centralizes the selection and interpretation of web content in GSEs; moreover, major GSEs are black-box systems, introducing vulnerabilities such as answer inaccuracies.


The nature of GSEs, which cite web content published by a wide range of actors, makes them vulnerable to poisoning attacks that inject malicious content onto the web and induce attacker-intended answers~\cite{poisonedrag-arxiv24, poisoning-web-scale-training-datasets-is-practical-sp24}. 
When GSEs generate answers lacking factuality, the cause is not only LLM hallucinations~\cite{sirens-song-in-the-ai-ocean-coli25, survey-of-hallucination-in-natural-language-generation-acmcsurv23} but also the lack of factuality in the web content obtained through web searches~\cite{retrieval-helps-or-hurts-deeper-arxiv24, poisonedrag-arxiv24, a-comprehensive-survey-on-trustworthy-recommender-systems-arxiv22}.
Web content can be published and modified by any user with any intent~\cite{poisoning-web-scale-training-datasets-is-practical-sp24, poisonedrag-arxiv24}.
Prior studies formalize poisoning attacks that place disinformation and misinformation on the web to generate attacker-intended answers in systems that retrieve from external databases and generate answers, including GSEs, because these systems can cite such content and generate text that reflects it~\cite{poisoning-web-scale-training-datasets-is-practical-sp24, poisonedrag-arxiv24, yu2025safetydevolutionaiagents}.
Specific to GSEs, prior studies show patterns in styles of web content that GSEs prefer to cite in answers and propose a method to optimize their own content to increase citation exposure~\cite{geo-apmr+24, wu2025generativesearchengineslikeai}.
Although they are beneficial for primary information providers that seek to increase the exposure of their web content as citations, they can also facilitate poisoning attacks.
This indicates that systematically evaluating the citation safety of GSEs against poisoning attacks is indispensable.

Existing evaluation criteria aim to assess two aspects: (1) how faithfully the cited content is reflected in the answers, and (2) how much the cited content dominates the answers.
Several studies evaluate \emph{faithfulness} by measuring the semantic consistency between the cited web content and the generated answers~\cite{citeeval-acl25, ragas-eacl24, ares-naacl24, evaluating-verifiability-in-generative-search-engines-emnlp23, enabling-llms-to-generate-text-with-citations-emnlp23, ranking-generated-summaries-by-correctness-acl2019, evaluating-the-factual-consistency-of-abstractive-text-summarization-emnlp20, alignscore-acl23, feqa-acl20}.
Prior studies also evaluate the \emph{domination} score, which represents the proportion of cited text relative to the total text volume of the generated answer~\cite{geo-apmr+24, wu2025generativesearchengineslikeai}.
By combining these metrics, we can measure how much a cited source has the power to influence the answer to a given question.
However, these studies alone cannot capture the attack surface of GSEs against poisoning attacks.
\emph{Faithfulness} studies target systems called \emph{RAG systems}, which retrieve from curated, fixed, and closed external authoritative databases to generate answers.
In contrast, GSEs treat the web as an external database that is open to anyone and dynamically updated, allowing attackers to easily inject malicious content that GSEs can cite.
Although the \emph{domination} score is designed for the GSE context, it only measures the degree of influence between cited content and the generated answer.
Because of these differences, existing evaluation criteria alone are insufficient to assess the attack surface.
To reveal the potential attack surface, we need to consider the perspective of which publishers GSEs cite in generated answers, not only the relation between cited content and answers.

% Prior studies of GSEs assess which cited content dominates the generated answers.
% In GSEs, a major evaluation criterion is the domination score, which represents the proportion of cited text relative to the total text volume of the generated answer~\cite{geo-apmr+24, wu2025generativesearchengineslikeai}.
% However, the domination score alone also cannot capture the attack surface for the same reasons as faithfulness, as it is a content-driven evaluation that does not consider publishers of cited content.

Moreover, existing citation evaluation also does not consider the impact of personalization on citation behavior~\cite{kearney2025languagemodelschangefacts, exploreing-safery-in-personalization-arxiv2026}.
The LLM applications actively personalize inference to improve user experience~\cite{openai2024memory, anthropic2025memory, google2026personal}.
In political domains, a user's political ideology influences answer generation in LLMs without web search mode~\cite{political-bias-audit-arxiv-2026, miyazaki_hall_2026_japan_ai_voting_advice}.
However, how personalization influences the selection of citations in GSEs remains insufficiently explored.
To reveal the attack surface of GSEs, we need to consider the effects of personalization on their citation behavior.

To address these gaps, we introduce a novel framework to characterize the potential attack surface of GSEs against poisoning attacks.
Our framework classifies each citation of answers by GSEs into \emph{content-injection barrier}, categorized as low, medium, or high, based on the practical difficulty of publishing content on the web with a given level of publisher authority.
In addition, the framework evaluates the faithfulness score and domination score across different content-injection barriers to validate the identified potential attack surfaces in specific scenarios.
% By combining these evaluation criteria, our framework estimates the potential attack surface susceptible to poisoning attacks from the citation behavior of GSEs.

We conduct experiments on three major GSEs (OpenAI GPT-5, Claude Sonnet 4, and Gemini Flash 2.5 with search mode enabled) in the United States and Japan.
We use $33$ question templates across $13$ parties, $3$ user profiles, and $3$ GSE models, totaling $3{,}861$ generated answers.
To retrieve GSE answers, we set a user profile that varies the user's level of political knowledge and ideology, and pose political questions to GSEs.
This enables systematic analysis of personalization's effect on citation behavior.

Our experiments reveal four findings.
First, each GSE has a distinct attack surface: some GSEs concentrate citations on primary information sources and exclude low-barrier sources, while others cite low-barrier sources more frequently.
Second, when citations contain few primary sources, web search results tend to include fewer primary sources and more low-barrier sources.
This suggests that the web search functionality of GSEs (e.g., query generation by LLMs) shapes the potential attack surface, rather than the LLM's preference for which sources from web search results to cite.
Third, answers to ruling party questions rely more on sources with lower content-injection barriers than answers to opposition party questions, making the ruling side more vulnerable.
Lastly, in contrast to biases arising from the LLM's internal knowledge, user profiles have little influence on the citation barrier pattern, faithfulness, or domination score across content-injection barriers.

Our main contributions are as follows:
\begin{itemize}
    \item We propose an evaluation framework of GSEs to characterize the potential attack surface against poisoning attacks.
    As a technical contribution, the framework classifies citations of answers by GSEs into \emph{content-injection barrier}, and evaluates the potential attack surface along three axes: barrier distribution, faithfulness, and domination score.
    \item We conduct experiments on three major GSEs in the United States and Japan in the political domain, using $33$ question templates across $13$ parties, $3$ user profiles, and $3$ GSE models for a total of $3{,}861$ generated answers.
    \item We find that the potential attack surface differs by the models and by whether the party in question is in the ruling or opposition position, but not by user profile.
\end{itemize}

