\section{Related Works and Motivation}
\label{sec:related}
This section introduces poisoning attacks on \emph{RAG systems}, summarizes key evaluation criteria, and highlights the challenges we identify for GSEs.

\subsection{Vulnerabilities of GSEs}
We introduce poisoning attacks on GSEs.
Zou et al.~\cite{poisonedrag-arxiv24} reveal and formalize an attack method called \emph{PoisonedRAG} that exploits \emph{RAG systems} to generate attacker-intended answers by placing malicious content into external databases.
Even if attackers can inject a small volume of malicious text into external databases, \emph{RAG systems} can produce attacker-intended answers for specific questions.
This malicious content includes text that attackers want displayed as answers to specific questions, especially false information such as ``\textit{OpenAI's CEO is Tim Cook.}''
PoisonedRAG attacks target closed-ended questions like ``\textit{Who is the CEO of OpenAI?}'' rather than open-ended questions like ``\textit{What are the latest trends in AI?}''~\cite{poisonedrag-arxiv24}.

In fact, several studies support the effectiveness of this attack.
Chen et al.~\cite{chen2022rich} show that in \emph{RAG systems}, when content containing two different claims (e.g., \textit{OpenAI's CEO is Tim Cook.} and \textit{OpenAI's CEO is Sam Altman.}) is placed and answers are generated for each claim, the answers may include each respective claim.
Wang et al.~\cite{wang2025ragconflictevidence} and Liu et al.~\cite{liu2025conflicts} demonstrate that even when there is an imbalance in the volume of supporting documents for each claim, \emph{RAG systems} tend to favor the answer with more supporting evidence, yet the underrepresented claim can still appear in responses.
These studies support the effectiveness of PoisonedRAG attacks and demonstrate that RAG may cite malicious content even when attackers place only a small volume of it.

To succeed in a poisoning attack, the malicious content must satisfy two conditions: \emph{Retrieval Condition} and \emph{Generation Condition}.
Retrieval Condition means that malicious content (such as text or HTML placed by attackers) is selected as top-$ k $ relevant content through retrieval tasks for target questions.
In GSEs, Retrieval Condition means that content on the web is retrieved as web pages ranked highly in search engine results by the search engine.
Generation Condition means that the content is used as reasoning knowledge in the LLM and reflected in the generated answers.
Aggarwal et al.~\cite{geo-apmr+24} propose \emph{generative engine optimization} (GEO), a method that optimizes website text structure and content from the perspective of Generation Condition to increase the exposure of web page content as citations in answers when the website passes the Retrieval Condition.
GEO provides theoretical evidence that GSEs are vulnerable to poisoning attacks.

% PoisonedRAG attacks are closely tied to actual influence operations.
% Many case studies on democratic countries show that false or misleading information intentionally placed on the web has influenced elections and political discussions.
% In U.S. presidential elections, large-scale information manipulation by Russia has been observed across multiple social media platforms. 
% Badawy et al.~\cite{badawy2018analyzing} and Zannettou et al.~\cite{zannettou2018disinformation} analyzed the 2016 election and showed that Russia-linked troll accounts orchestrated disguised activities across multiple social media platforms.
% For the 2024 election, Cinus et al.~\cite{cinus2025cross} revealed that coordinated inauthentic activities and Russia-linked media content continue to systematically spread across social media platforms.
% In Japan, during the 2024 and 2025 elections, troll and bot accounts from outside Japan posted disinformation and manipulated narratives on social media platforms, amplifying the claims of specific political parties and shaping public opinion~\cite{nikkei2025sanseito,nippon2025russian}.
% In 2025, OpenAI reported that accounts linked to Chinese authorities used LLMs to generate false claims against politicians~\cite{openai2026disrupting}.
% Therefore, the act of attackers placing malicious content on the web to influence voter perception through GSEs will be a real threat.

\subsection{Citation Evaluation}
\label{subsec:citation_evaluation}
We first introduce seminal studies that aim to evaluate \emph{RAG systems}.
These studies highlight that in ideal retrieval-and-generation systems, all claimed sentences in an answer are supported by external sources from databases as \emph{citations} and the sentences with citations accurately and faithfully reflect the claims.
To evaluate these systems, the key evaluation metrics are \emph{faithfulness} and \emph{domination}.

\emph{Faithfulness} measures how accurately the generated answer reflects the content of its citations~\cite{citeeval-acl25, ragas-eacl24, ares-naacl24, evaluating-verifiability-in-generative-search-engines-emnlp23, enabling-llms-to-generate-text-with-citations-emnlp23, ranking-generated-summaries-by-correctness-acl2019, evaluating-the-factual-consistency-of-abstractive-text-summarization-emnlp20, alignscore-acl23, feqa-acl20}.
Faithfulness is typically computed by three methods: entailment-based~\cite{ranking-generated-summaries-by-correctness-acl2019, true-reevaluating-factual-consistency-arxiv22, evaluating-the-factual-consistency-of-abstractive-text-summarization-emnlp20, alignscore-acl23}, similarity-based~\cite{bertscore-arxiv20, bartscore-neurips21}, and QA-based~\cite{feqa-acl20}.
Similarity-based methods are most appropriate for calculating reflection accuracy.
Similarity-based methods quantitatively measure semantic similarity between two texts and rely on neural encoder models.
Zhang et al.\ show that similarity-based methods achieve higher precision than entailment-based and QA-based methods in tasks evaluating consistency between long documents and their summaries~\cite{finegrainedcitationevaluationgenerated-arxiv24}.
This approach aligns with GSE behavior of summarizing web page content retrieved from search results and generating answers with citations.
Citation evaluation applies these faithfulness evaluation methods to each sentence $ l_i $ of generated answer $ r $ with citations $ C_i $, and evaluates reflection accuracy for the entire answer $ r $.

\emph{Domination} measures the proportion of cited text relative to the total text volume of the generated answer~\cite{geo-apmr+24, wu2025generativesearchengineslikeai}.
For each citation $ C_i $, they count the number of words in the sentences to which $ C_i $ is attached and report this count as a proportion of the total number of words in the generated answer $ r $.
This is a major metric for evaluating the influence of citations in GSEs~\cite{geo-apmr+24, wu2025generativesearchengineslikeai}.
Aggarwal et al.~\cite{geo-apmr+24} also propose a domination evaluation method that measures the influence of citations on generated answers in the GSE context.

However, they do not assess the authority and trustworthiness of cited content, as they disregard the publisher of those sources.
Such content-driven evaluations leave a gap between the seminal studies on \emph{RAG systems} and their applicability to GSEs for revealing the potential attack surface of poisoning attacks.
In \emph{RAG systems}, poisoning attack studies focus on how much malicious content attackers need to inject into external databases to succeed in a poisoning attack.
In contrast, GSEs retrieve information from the open web, where attackers can inject malicious content more easily than in \emph{RAG systems}.
This ease of injection can enable a successful poisoning attack as previously described.
The main concern shifts from preventing malicious content from existing in external databases to preventing the system from incorporating even a small amount of malicious content injected by attackers during web searches.
Unlike \emph{RAG systems}, GSEs operate under the assumption that malicious content is always present in their external sources (i.e., the open web), and therefore existing evaluation methods alone are insufficient to assess the safety and quality of GSEs.


\subsection{Authority and Trustworthiness}
Several studies propose methods to improve the inclusion of authoritative sources in citations generated by \emph{RAG systems} and GSEs~\cite{zhou2025trustragenhancingrobustnesstrustworthiness, lee2026relevanceauthorityauthorityawaregenerative}.
TrustRAG~\cite{zhou2025trustragenhancingrobustnesstrustworthiness} identifies and removes malicious documents during content retrieval by clustering candidate documents and matching them with the internal knowledge of the LLM.
AuthGR~\cite{lee2026relevanceauthorityauthorityawaregenerative} computes an authority score for web pages using a vision-language model that evaluates both the textual content of the page and visual features extracted from page screenshots, such as layout quality, design, and advertisement density. 
The system prefers to cite web pages with high authority scores.

However, evaluating only the content itself of citations is insufficient for assessing the safety of GSEs under poisoning attacks.
As described in Section~\ref{subsec:citation_evaluation}, because anyone can publish content on the web, attackers can deliberately optimize the scores of content-based evaluation metrics while still injecting malicious information into the web.
In fact, the ``Doppelganger'' operation reported by EU DisinfoLab~\cite{eudisinfolab2022doppelganger,foreignaffairs2024doppelganger} shows that more than $700$ fake news websites were created by imitating the domain names and designs of legitimate media, and their content was distributed while disguised as legitimate media.
Such legitimate-looking malicious content undermines approaches that evaluate only the content itself, causing both false negatives and false positives.
Therefore, for GSEs, we need to evaluate not only the content itself of citations, but also the authority and trustworthiness of content publishers.

Furthermore, they typically assume the presence of poisoning attacks on \emph{RAG systems} and primarily focus on developing defenses or system improvements. 
However, they do not provide a systematic understanding or measurement of the actual extent of citation selection bias and vulnerability found in production GSEs.


\subsection{Personalization of LLMs}
\label{sec:related_works_personalization}
Personalization is a key factor in improving the user experience of chat-based applications~\cite{openai2024memory, anthropic2025memory, google2026personal} and is a recognized research direction for language models~\cite{salemi2024lamp, mysore2024pearl}.
In personalization, the general approach is to embed the user's attribute information together with the user's question.
This approach enables the applications to generate answers that more accurately reflect the user's preferences, background, and needs.

Several studies investigate how personalization affects answers generated from the internal knowledge of LLMs.
Kearney et al.~\cite{kearney2025languagemodelschangefacts} show that across several domains, answers change systematically depending on user attributes such as race, gender, and age.
The influence of user attributes also extends to tasks that have objectively correct answers.
Vijjini et al.~\cite{exploreing-safery-in-personalization-arxiv2026} show that LLM response performance varies systematically even in tasks such as mathematical reasoning, general knowledge, and programming.

This effect also extends to the user's political ideology.
Tornberg et al.~\cite{political-bias-audit-arxiv-2026} analyze political ideology bias in representative and widely used LLMs.
The study shows that LLMs produce opposition-leaning answers by default and LLMs shift strongly toward the ruling party for conservative users but only slightly toward the opposition party for progressive users, showing an asymmetric response to personalization.
Miyazaki et al.~\cite{miyazaki_hall_2026_japan_ai_voting_advice} show that a similar pattern holds in the Japanese language and Japanese political context.
They show that when users do not indicate their policy positions, LLM answers lean toward the ruling party, whereas when users explicitly indicate their political stance, the answers shift substantially in that direction.

However, these prior studies focus on biases that arise from the internal knowledge of LLMs and do not examine biases in GSEs. 
To the best of our knowledge, no prior study has examined how personalization affects the citation behavior of GSEs, including aspects such as source authority and trustworthiness, and domination and faithfulness of citations.

\subsection{Research Motivation}
To understand the potential attack surface of GSEs, our goal is to build a novel evaluation framework. 
Our framework introduces new evaluation criteria centered on the publisher attributes of citations in generated answers, enabling a systematic assessment of the underlying attack surfaces and the resilience of GSEs against poisoning attacks.
We focus on establishing evaluation criteria for the attack surface of GSEs to poisoning attacks. 
We do not aim to demonstrate practical attacks or identify actual malicious content.

Specifically, our framework addresses the following research questions:
\begin{description}
  \item[\textbf{\textit{R-1}}] Which publishers' content do GSEs prefer to cite, and does this reveal any bias in citation selection from the perspective of publishers?
  \item[\textbf{\textit{R-2}}] Which publishers' content has the power to influence the domination and faithfulness of citations?
  \item[\textbf{\textit{R-3}}] How does personalization affect the citation behavior of GSEs?
\end{description}

We apply our framework to the political domain, where GSEs increasingly mediate access to information essential to democratic processes.
Because the flow of information from political parties to citizens is a cornerstone of democratic electoral processes~\cite{the-trust-gap-young-peoples-tactics-for-assessing-the-reliability-of-political-news-ijpp22, kovach2007elements}, GSEs can substantially influence citizens' decision-making in elections~\cite{fisher2026biasedaiinfluencepolitical}.
Especially, focusing on the task of voters gathering information about specific political parties, we characterize the attack surface across political parties, ideologies, countries, and voter profiles (e.g., prior political knowledge and ideology).
Based on this analysis, we discuss where attackers could distort political information delivered through GSEs.

