\section{Experiment}
\label{sec:experiment}
We apply our framework to questions about U.S. and Japanese political parties on major GSE models, revealing their citation patterns and attack surfaces based on \emph{conjection injection barriers}.

\subsection{Experimental Setup}

\textbf{Tatget GSE Models.}
We employ three GSE models for answer generation: OpenAI GPT-5~\cite{chatgpt}, Claude Sonnet $4$ (claude-4-sonnet-20250514)~\cite{claude}, and Gemini Flash $2.5$ (gemini-2.5-flash)~\cite{gemini}, the most advanced publicly available models with web search mode enabled.
We clarify why we focus on closed GSE models in this study.
According to surveys~\cite{menlo-ventures2025stategenaienterprise, a16z2025stateconsumerai}, closed models dominate the LLM market in both enterprise and consumer segments, with Claude, OpenAI, and Gemini together accounting for 88\% of spending share, while open-source models account for only 11\%.
These models are developed in the U.S., but they dominate usage in Japan as well.
According to GMO Research \& AI~\cite{gmo-research2025japanai}, Japanese users predominantly rely on closed models such as GPT, Gemini, and Copilot, all of which are U.S.-developed products.
While Japan has developed numerous LLM models, to our knowledge, no Japanese GSE models are publicly available.
Furthermore, widely deployed GSEs such as Google AI Overview, which integrates Google Search by default, rely on the closed model Gemini~\cite{stein2025expandingaioverviewsaimode, reid2025aisearchbeyondinformation}; consequently, users routinely encounter generated answers from closed GSE models when conducting web searches, underscoring the central role these models play in contemporary information retrieval.
Note that our evaluation is not restricted to closed models, as it relies only on the inputs and outputs of GSEs (questions and answers), not their internal states.
For reproducibility, the question-answer datasets are available in our repository~\cite{QL_CIKM_RERO}.

In our experiments, the temperature of each GSE model cannot be set because APIs do not allow setting temperature for LLMs with search mode enabled; thus, the cited web sources and textual content of answers vary across generations.
To capture answer variation, we ask each question three times to suppress bias from a single answer.
The answers are obtained on May $5$, $2026$.


\textbf{User Profiles.}
We design three user profiles based on two user attributes: \textbf{political knowledge}, which represents the user's familiarity with political issues and takes the levels \textsc{Unknown} and \textsc{High}; and \textbf{political ideology}, which represents the user's political leanings and takes the levels \textsc{Conservative}, \textsc{Progressive}, and \textsc{Neutral}.

Using these attributes, we construct three user profile combinations: \textsc{Unknown-Neutral}, \textsc{Unknown-Progressive}, and \textsc{High-Progressive}.
The \textsc{Unknown-Neutral} profile represents a user with no political knowledge and a neutral ideology; the \textsc{Unknown-Progressive} profile represents a user with no political knowledge but a progressive ideology; and the \textsc{High-Progressive} profile represents a user with high political knowledge and a progressive ideology.

\textbf{Questions.}
We design political questions on topics common to both countries to elicit policy positions in a politically neutral manner, focusing on whether GSEs cite contents articulating positions on the target topics rather than favoring any particular party.

All questions are closed-ended and include a party name according to PoisonedRAGs study (e.g, ``Regarding government debt, does {PARTY} currently prioritize debt restraint or growth-oriented investment?'').

To avoid bias, we build the question set on MARPOR (Manifesto Project), an established political-science framework for classifying party manifestos.
From the four voter-facing MARPOR domains most relevant to everyday political judgment (External Relations, Economy, Welfare and Quality of Life, Fabric of Society), we select 11 topics on which all target parties take an explicit stance; the full list is given in Appendix~\ref{app:appendix_topics}.
Using these 11 topics as input, we prompt three closed-weight LLMs to generate candidate questions and curate the final set of 33.
Questions and answers are written in English for U.S. parties and in Japanese for Japanese parties.
The full question set is available in our repository~\cite{QL_CIKM_RERO}.

Following the DETAIL framework of Kim et al.~\cite{kim2025mattersmeasuringimpactprompt}, we fix question specificity at the least specific domain-level (asking about a stance on an entire policy domain without proper nouns or concrete figures).
This prevents questions and citations from being skewed toward topics that specific publishers actively promote, and reflects the abstraction level typical of voters' everyday political judgments.


\textbf{Target Political Parties.}
We target political parties satisfying each country's requirements for national political parties as primary information sources.
Specifically, in Japan we target eight parties. The ruling parties are ``Liberal Democratic Party (LDP)'' and ``Japan Innovation Party (JIP)'', and the opposition parties are ``Centrist Reform Coalition (CRA)'', ``Democratic Party for the People (DPP)'', ``Japanese Communist Party (JCP)'', ``Reiwa Shinsengumi (Reiwa)'', ``Sanseito'', and ``Conservative Party of Japan (CPJ)''. In the U.S., we target five parties. The ruling party is ``Republican Party (GOP)'', and the opposition parties are ``Democratic Party (DP)'', ``Green Party (GPUS)'', ``Libertarian Party (LP)'', and ``Constitution Party (COP)''.


\subsection{Experimental Results}


\textbf{Distribution of Content-injection Barriers in Answers}

we defer discussion of desirable citation balance for GSEs to Section~\ref{sec:discussion}.

This sub-experiment answers which publisher attributes from the perspective of content-injection barriers GSEs preferentially cite (\emph{R-1}).
% To do this, we use citation classification and distribution of content-injection barriers method in Section~\ref{subsec:citation_classification}.
We calculate the proportion of each content-injection barrier using the citation classification method in Section~\ref{subsec:citation_classification} as $ P_{\lambda_i} = |C^{\lambda_i}|/|C| $, where $ |C^{\lambda_i}| $ is the number of citations in content-injection barrier $ \lambda_i $ and $ |C| $ is the total number of citations.

We first analyze the overall trends in citation patterns.
Overall, for Japanese questions (Japanese parties), all three models show a high proportion of target-party primary information sources, accounting for about $60\%$: OpenAI $63.0\%$, Gemini $60.9\%$, and Claude $60.9\%$.
In contrast, for U.S. questions (U.S. parties), the proportion of primary information sources decreases (OpenAI $43.9\%$, Gemini $27.0\%$, Claude $28.1\%$), and the proportion of secondary information sources increases.
We observe a large structural difference: primary source dependence in the Japanese setting and external source dependence in the U.S. setting.

\textbf{Qualitative Analysis:}
We discuss qualitative insights from the analysis in Section~\ref{sec:experiment}.
The distribution difference in citations from high content-injection-barrier sources (academia and government) between Japan and the U.S. is notable.
Focusing on web pages cited in U.S. questions, we find that a high percentage of citations came from the ``www.presidency.ucsb.edu'' domain ($29.0\%$ in OpenAI, $23.2\%$ in Gemini, $47.8\%$ in Claude).
This web content is owned by the American Presidency Project, a nonpartisan academic archive at the University of California, Santa Barbara, that collects, preserves, and provides public access to official documents, speeches, and records related to the U.S. presidency.
Because the archive stores and publishes factual information, such as public papers and speech transcripts, with minimal editing, the content could be compatible with LLMs for interpreting and reasoning.
The high percentage of citations from external low content-injection barrier sources in the U.S. could reflect the accessibility of unedited public web content.

The number of web search hits also provides insight into the tendency for ruling parties to cite fewer primary information sources.
When entering only the party names of Japanese parties in the Google search engine, the number of search hits was $47{,}100{,}000$ for LDP, the ruling party throughout successive administrations, whereas the others averaged $8{,}566{,}250$.
This suggests that the entire proportion of primary information sources on the web related to LDP is relatively smaller than other parties, resulting in the small proportion of primary information sources in citations.
For U.S. parties, Republican Party and Democratic Party, which are the two parties that have alternated as the ruling party throughout history, $165{,}000{,}000$ and $399{,}000{,}000$ search hits were found, respectively.
However, the Green Party of the U.S. had $2{,}190{,}000{,}000$ search hits, substantially exceeding the two major parties, while maintaining a high proportion of primary information sources in GSE citations.
This suggests that the amount of information about the target topic is somewhat related to cited primary information, with a counterexample indicating that information-provider strategy can suppress this relationship.



\textbf{Distribution of Citation Grounding Score by Content-injection Barriers}
This sub-experiment answers which publisher attributes from the perspective of content-injection barriers GSEs preferentially and faithfully ground in generated answers (\emph{R-2}).
% To do this, we use the Citation Grounding Score in Section~\ref{subsec:citation_grounding}.
For each answer $r$ under all grounding bands $b$ and content-injection barrier $\lambda_i$, we calculate the total count $N^{(b)}_{\lambda_i} = |\{c_i \in C \mid \textsc{CIB}_{\mathcal{P}}(c_i) = \lambda_i, \textsc{CGS}(c_i, r) = b\}|$ and proportion $P^{(b)}_{\lambda_i} = N^{(b)}_{\lambda_i}/\sum_{\lambda} N^{(b)}_{\lambda}$ within each band using the classification method $\textsc{CIB}_{\mathcal{P}}(c_i)$ in Section~\ref{subsec:citation_classification} and the Citation Grounding Score $\textsc{CGS}(c_i, r)$ in Section~\ref{subsec:citation_grounding}.
We examine overall trends in citation grounding coverage across similarity bands.
Comparing the distribution of the coverage between questions about Japanese and U.S. parties, we find that, in both settings, the proportion of highly reliable sources such as primary information sources and high-barrier sources has the greatest coverage in high-similarity bands, whereas the share of opponent and secondary information with medium to low barriers shrinks.
This tendency is common to all models, indicating that high-similarity citations are more strongly supported by primary or high-barrier information.
In contrast, in the low-similarity bands, references originating from opponent and secondary information sources with medium to low barriers are prominent, forming a citation structure where the link between answer sentences and cited sentences is weak.

We analyze model-specific characteristics in citation coverage.
Clear differences exist in the distributions by model.
In the U.S., the $\geq 0.90$ band expands in all models, securing high similarity not only with primary information sources but also in parallel with opponent sources and high-barrier sources.
In Japan, however, OpenAI has a notably narrow $\geq 0.90$ band, with most citations concentrated in the low-similarity band ($[-1.0, 0.8]$).
Gemini shows the clearest tendency to increase the proportion of primary information sources and decrease that of low-barrier sources as the similarity rank increases.
Claude forms high-similarity bands as the main component in both countries; in Japan, primary information sources dominate the high-similarity bands, whereas in the U.S., medium- to high-barrier sources contribute substantially, making co-existence with opponent and secondary information sources conspicuous.

We compare citation coverage patterns between Japan and the U.S.
With questions about Japanese politics, all models show a tendency to increase the proportion of primary information sources and decrease those of low- to medium-barrier sources as the similarity rank increases.
With questions about U.S. politics, by contrast, even in the high-similarity bands the shares of opponent and secondary information sources such as medium- and high-barrier sources are large, and the share of primary information sources is limited.
This difference likely reflects the depth of policy explanations on official party domains and differences in the surrounding external knowledge infrastructure (e.g., government statistics, think tanks, major media, aggregation platforms), as discussed in Section~\ref{sec:api_response}.

These results show that citation coverage serves not merely as a similarity metric but, by indicating which publisher attribute categories have the power to generate the answer, can reveal a model's strategy and the characteristics of the information ecosystem by country.
In Japan, high similarity tends to be supported by dependence on target-party primary information sources, whereas in the U.S., high-barrier opponent and secondary information sources actively contribute to the formation of high similarity.
